### 2018-08-25 abstract.tex
Abstract have been re-written #5

Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced 
demand for tools to analyze these systems. This paper introduces a Python 
script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the 
changing isotopic composition of an irradiated fuel salt. SaltProc couples with 
the Monte Carlo code, SERPENT 2, for neutron transport and depletion 
calculations. SaltProc capabilities was illuminated for full-core depletion in 
the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could 
be achieved after 16 years and (2) the multiplication factor stabilizes after 6 
years of operation. Fuel salt irradiation with online reprocessing causes 
considerable neutron energy spectrum hardening; this spectral shift has a 
problematic impact on safety parameters (e.g., temperature reactivity feedback, 
reactivity control system worth). Volatile gases and noble metals removal has 
positive effect on the core performance approximately 7500 pcm over 10-years 
timeframe; rare earth elements removal has slower rate and less impact on 
reactivity (5500 pcm). Finally, the average $^{232}$Th feed rate throughout 60 
years of operation is 100 g/GWh$_e$ which is a good agreement with other recent 
research. Problematic effects of neutron energy spectrum hardening during 
\gls{MSBR} operation should be taken into account for neutronics, 
multi-physics, and fuel cycle performance analysis.

>>>>

Nowadays climate change pushes humankind in search new ways to generate carbon-free, reliable, nonintermittent base load power. That is reason why interest in advanced nuclear energy and, particularly \glspl{MSR} has resurged, with multiple new companies pursuing commercialization of \gls{MSR} designs\footnote{Examples include both liquid-fueled and solid-fueled molten salt designs from
Transatomic, Terrapower, Terrestrial, Moltex Energy, and Thorcon.}. To further develop these \gls{MSR} concepts researchers need tools for analyzing liquid fueled molten salt reactor depletion and fuel processing. However, most contemporary nuclear reactor physics software is unable to perform high-fidelity full-core depletion calculations in an online reprocessing regime. This paper introduces a Python script, SaltProc, which couples with the Monte Carlo code, SERPENT2, and simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt. SaltProc capabilities was demonstrated for full-core high-fidelity model of the commercial \gls{MSBR} concept and compared well to previous results from lower fidelity analyses.
